Title?

### 2018-05-05 paper_wc.tex
Topology of best-reply

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} S_i^j(s_{-i})$ the
set of opponent profiles. We assume that the users are connected.
A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. We assume
that users are selfish, and therefore rational. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

@@

In a multi-auction market, each auction a buyer joins has the potential to
decrease the potential cost of its data. However, increasing the size of the
auction implies a certain risk, which we may interpret as a potential and
definite
liability. Increasing the number of transactions causes additional messaging
overhead, fees, and increased competition from other buyers. 
A transaction also causes potential indirect costs, which may be considered work done to find
sellers, or effort of communication from participation. A seller
has the potential for greater profit with each new buyer in its auction, taking 
the same risk.
%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
%and the individual. We denote the potential indirect costs of participation of
%each user as $\varrho$.
The liability of any user is naturally absorbed into the bid fee $\epsilon$,
as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
dependent on the association between two users and their market positions, in
addition to the underlying network structure. Now, both sellers and buyers must consider
the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)

@@

We further determine that the set of buyers and sellers participating
in a single equilibrium is bounded by the potential indirect costs of
participation. We will denote this individual cost to each user as
$\varrho$. The indirect cost is the portion of the bid fee
$\epsilon$ that is dependent on the underlying network and the individual.
Observing that $\varrho$ indirectly effects user utility,
and therefore acts to establish a natural budget for each user. We give this
constraint as, 
\begin{equation}\label{poolbnd}
    u \le \varrho,
\end{equation}
which may be interpreted as the effort a rational user is willing to expend
on its message space, and serves to limit the size of the buyer/seller pools.

@@

The property of truthfullness is an essential component of equilibrium in
second-price markets. The strategies described in this paper have removed the
necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
construction of the user strategy space results in truthful bids that are optimal for all users,
i.e. bid prices are to the marginal value as determined by market dynamics. 
To achieve incentive compatibility, we find that the opt-out buyer must choose
this subset so that its overall marginal value is greater than its market price.
We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
has incentive to change its bid as a result of a market shift or partial
allocation. We now show the necessary condition of a truthful reply, new bid
prices must differ from the last by at least $\epsilon$, and prove that the
resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
In a truthful reply, the term $\epsilon/\theta_i'(0)$
ensures that a new bid price differs from the last bid price by at least
$\epsilon$, thereby ensuring that a buyer does not change its bid without
correcting the effects of unstable shifts.
We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
there exists a market equilibrium extending over a subset of connected
local markets. 
For a buyer $i$, define have the set of possible $\epsilon$-best replies,
\begin{equation}\label{e-bid}
    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
\end{equation}
and the set of \emph{truthful} bids, 
\begin{equation}\label{t-bid}
    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
\wedge p_i = \theta_i'(z)\rbrace,
\end{equation}
where $\wedge$ denotes the logical ``and" operator. The ``strategic" set $T_i$
is restricted by Proposition \ref{buyerstrategy}. In the remainder of our
analysis we limit the strategy space to our construction, and so we have the
bid for buyer $i$, $S_i=\Pi_{j\in\mcI_i} S_i^j$, and the opponent bid, $S_{-i}
=\Pi_{j\in\mcI_i} S_i^j(s_{-i})$ 
We have the following Proposition,

@@

We have proven that buyers will submit bids according to their marginal
valuations. Now, in the interest of completeness (BAD SENTENCE), we extend our result to be
all-inclusive. As a result of the PSP multi-auction in the constructed strategy
space, we find a well-defined mathematical structure manifests as a result of bid
correspondence. The game-theoritical basis of our argument is complemented by,
and benefits by (NEED? extension to) an abstract-theoretical analysis.
Motivated by the symmetric nature of supply and demand we provide further rigor
by mathematical construction. Thus, we begin with the definition of
correspondence,
{
\definition{(Correspondence)}
An ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
$Y$, i.e. any subset of the Cartesian product $X\times Y$.
}
Now, in an economic model, the mapping $(\mcI,\mcI,R)$ is a map from the
elements of $\mcI$ to the power set $\mathcal{P}(\mcI)$. The most obvious
example of a correspondence in our model is the buyers' best response
$B_i^\epsilon$, where, for the multi-auction,
$\Pi_{j\in\mcI} S_i^j$ and $\Pi_{j\in\mcI} S_{-i}^j$ are power sets under the
identity relation, e.g $(S_i, S_i,\Pi\in\mcI S_i)$. The auction
progresses by repeated mappings, where the full strategy space is the
correspondence
$(\Pi_{j\in\mcI}S_i,\Pi_{j\in\mcI}S_{-i},\Pi_{j\in\mcI}S_i^\epsilon)$ and
finally, the best response is given as a reaction correspondence $B_i^\epsilon$
defined by the mixed-strategy game.

Thus, we address the sellers bids, and include the following corollary to support our result.
{
\corollary{Data-bid correspondence (seller cooperation)}
For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is (NEED THIS? consistent with) a truthful
$\epsilon$-best reply.
}\\
\textbf{Proof:}
We claim there exists an equivalence relation $R$ that naturally evolves in the
strategy space. For a seller $j$, let $y=\theta_i'(\g_i^(a))$ for a buyer $i$. We have that, for any allocation $a$, 
\begin{equation}\label{eqrel}
        R \equiv (\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))) = (\g_i^j(a),y),
\end{equation}
defines equivalence $i \thicksim j$, where we use the definition of set
equality based on first-order logic with equality. By definition, 
$\forall \ i, \ \forall \ j, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
\Rightarrow i \thicksim j$. This is the converse of (\ref{jtoi}). Formally, the
axiom states that a set is \emph{uniquely} determined by its members.
$R$ is defined by the bid price and
reserve price of buyer $i$ and seller $j$, respectively. We
have, for any $z\ge 0$,
\begin{equation}\label{eqrel}
        R \equiv i\thicksim j \equiv \theta_i'(z) - {\theta^j}'(z)\ge\epsilon
\end{equation}
defines equivalence $i \thicksim j$. Equivalence class $[i]$ is by definition
the market supply at the buyers' valuation $\theta_i'$. Clearly, $k\thicksim k,
\ \forall \ k\in\Delta$, and $\epsilon \ge \theta_i'(z) - {\theta^j}'(z)$
%, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
%and cannot sell more data than the buyers' aggragated bid quantities.
The result follows by symmetry, and as the buyers' bids are
truthful, and by (\ref{newprice}),Lemma \ref{userunion} and Lemma
\ref{buyercoordinate}.$\qed$\\

The ease by which the game is constructed is a consequence of the the cartesian
product on a 2-dimensional message space.

The reserve price $\epsilon$ acts as a placeholder for a seller submitting an
auction to the ISP. As was proven in \cite{lazar}, the positive reserve price allows us to
restrict our analysis to continuous, truthful bids. The strategy space of
truthful bids is a collection of truthful bid, or ``strategy", vectors.
From the original proof by \cite{lazar}, we observe that the collection of
unconstrained truthful bids, $T_i = \Pi_{j\in\mcI} T_i^j$, may not be a subset
of the collection of $\epsilon$-best replies, $\Pi_{\in\mcI} S_i^\epsilon$.         
%An essential component of determining the existence of a Nash equilibrium is 
For this work, it suffices to show the continuity of the set of truthful
$\epsilon$-best replys, which we will denote $B_i^\epsilon = T_i\cap S_i^\epsilon$, in opponent bid profiles $S_{-i}$.

{
\lemma{(Continuity of $\epsilon$-best reply on $\Delta$)}
Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
}\\
\textbf{Proof:}
Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ \overline{P}])$
is a product of closed subsets of compact sets. Then, as a closed
subset of a compact set is compact, and by Tychonoff's theorem, $\g_i \circ
B_i^\epsilon$
is compact subset of $B_i^\epsilon$. Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
definition of $\Delta$ and the product, 
\begin{align*}
    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
[0,\overline{P}]\bigg)
    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
[0,\overline{P}]\bigg) \\
    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
\times \lambda^j \subset T.
\end{align*}
The result follows from the fact that $t_i$ is continuous in $s_i$, as was
proven in \cite{semret}, and as a finite union of compact sets is a compact set.
$\qed$
on any subset $\lbrace
s_{-i}\in S_i : \ \forall \ z > 0, \overline{P} \ge P_i(z,s_{-i}) \ge
\underline{P} \rbrace$, where $0<\underline{P}\le \overline{P} < \infty$
(HERE) The dimension of a linear space is defined as the maximal number of linearly
independent vectors or, equivalently, as the minimal number of vectors that span
the space

We now restrict our analysis to truthful $\epsilon$-best replies, $B^\epsilon$.

@@

We show that our bidding strategy is
part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
equilibrium, where the sellers reserve prices are fixed.
{
\lemma{(Static Nash Equilibrium)} 
Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
Using the rules of the data auction mechanism applied independently by each
user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
}\\
\textbf{Proof:}
(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
$T=\Pi_{k\in\Lambda^j} T_k$. Now, $t$
represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
and we may use Brouwer's fixed point theorem, as in \cite{semret},

@@

>>>>

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
set of opponent profiles. We assume that the users are connected.
A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. We assume
that users are selfish, and therefore rational. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

@@

We interpret the collection of local auctions as collection of congestion games,
where a buyers' payoff depends on the dynamics of the set of local auctions it
``chooses".
In a multi-auction market, each auction a buyer joins has the potential to
decrease the potential cost of its data. However, increasing the size of the
auction implies a certain risk, which we may interpret as a potential and
definite
liability. Increasing the number of transactions causes additional messaging
overhead, fees, and increased competition from other buyers. 
A transaction also causes potential indirect costs, which may be considered work done to find
sellers, or effort of communication from participation. A seller
has the potential for greater profit with each new buyer in its auction, taking 
the same risk.
%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
%and the individual. We denote the potential indirect costs of participation of
%each user as $\varrho$.
The liability of any user is naturally absorbed into the bid fee $\epsilon$,
as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
dependent on the association between two users and their market positions, in
addition to the underlying network structure. Now, both sellers and buyers must consider
the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)

@@

We further determine that the set of buyers and sellers participating
in a single equilibrium is bounded by the potential indirect costs of
participation. We will denote this individual cost to each user as
$\varrho$. The indirect cost is the portion of the bid fee
$\epsilon$ that is dependent on the underlying network and the individual.
Observing that $\varrho$ indirectly effects user utility,
and therefore acts to establish a natural budget for each user. We give this
constraint as, 
\begin{equation}\label{poolbnd}
    u \le \varrho,
\end{equation}
which may be interpreted as the effort a rational user is willing to expend
on its message space, and serves to limit the size of the buyer/seller pools. 
Additionally, in congestion games,
overly-frequent bid updates can result in an auction being
overloaded, similarly to a DOS (denial-of-service) attack, thus the
``liability" component of $\epsilon$ attempts to regulate bid flooding.

@@

The property of truthfullness is an essential component of equilibrium in
second-price markets. The strategies described in this paper have removed the
necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
construction of the user strategy space results in truthful bids that are optimal for all users,
i.e. bid prices are to the marginal value as determined by market dynamics. 
To achieve incentive compatibility, we find that the opt-out buyer must choose
this subset so that its overall marginal value is greater than its market price.
We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
has incentive to change its bid as a result of a market shift or partial
allocation. We now show the necessary condition of a truthful reply, new bid
prices must differ from the last by at least $\epsilon$, and prove that the
resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
In a truthful reply, the term $\epsilon/\theta_i'(0)$
ensures that a new bid price differs from the last bid price by at least
$\epsilon$, thereby ensuring that a buyer does not change its bid without
correcting the effects of unstable shifts.
We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
there exists a market equilibrium extending over a subset of connected
local markets. 
For a buyer $i$, define the set of possible $\epsilon$-best replies,
\begin{equation}\label{e-bid}
    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
\end{equation}
and the set of \emph{truthful} bids, 
\begin{equation}\label{t-bid}
    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
\wedge p_i = \theta_i'(z)\rbrace,
\end{equation}
where $\wedge$ denotes the logical ``and" operator. We note that the ``strategic" set $T_i$
is restricted by Proposition \ref{buyerstrategy}.
We have the following Proposition,

@@

The strategy space of is comprised of a collection of bid, or ``strategy", vectors that
together, describe the collection of congestion games. A change in buyer $i$'s
utility, resulting from a change in strategy, equals the change in
the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
formulated by mapping the incentives of all users in a local auction to a
single function. The goal of our analysis is to therefore construct a global potential function that encompasses
all local markets. Then, we may determine a Nash equilibrium by finding a local
optima of the potential function. Additionally, as the potential function also
iterates, it may be used in an analysis of convergence. The
convergence of a Nash equilibrium results from the progression of
$\epsilon$-best replies, where each subsequent bid is a unilateral
improvement, provided that $t_i$ is continuous in opponent profiles.
From the original proof by \cite{lazar}, we observe that the collection of
unconstrained truthful bids may be a subset
of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
%An essential component of determining the existence of a Nash equilibrium is 
For this work, it suffices to show the continuity of the set of truthful
$\epsilon$-best replies in the set of opponent bid profiles.
In order to address continuity in a global sense, we must demonstrate
continuity in the construction of our model.
Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
and determine the
existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
correspondence,
{
\definition{(Correspondence)}
A correspondence is mathematically defined as an ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
$Y$, i.e. any subset of the Cartesian product $X\times Y$.
}

In an economic model, a correspondence $(S_i,S_{-i},R)$ defines a map from $S_i$
to the power set $S_{-i}$, where $R$ is a binary relation, i.e. $R \subset
S_i\times S_{-i}$. The classic
example of a correspondence in our model is the buyers' best response
$B_i^\epsilon$, where, for the multi-auction,
$S_i$ and $S_{-i}$ are built by repeatedly using the
cartesian product over bid profiles. The power set 
$S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
product of ordered sets. 
The best response is a reaction correspondence
defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
profiles $S_{-i}$. \\
\textbf{Remark:} 
The ease by which the game is constructed is a consequence of the the cartesian
product on a 2-dimensional message space. \\
A natural induced topology of this space is the product
topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.

Motivated by the symmetric nature of supply and demand, we determine the
game-theoritical argument is complemented by an abstract-theoretical analysis.
In fact, we may even be philosophically motivated, as the truth value of a bid
is determined only by how it relates to markets, and whether it provides an
accurate correspondence. Using a set-theoretical approach to address the sellers
bids, we derive our result from the symmetry of supply and demand,
(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
\ref{buyercoordinate}, and include the following corollary,
{
\corollary{Data-bid correspondence (seller cooperation)}
Let $\Delta$ be defined as in Lemma (\ref{userunion}).
For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
$\epsilon$-best reply.
}\\
\textbf{Proof:}
We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
We use the the axiom of set equality,
based on first-order logic with equality, which states that,  
$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
Then, for any allocation $a$, we may define the relation, $i\thicksim
j$,
\begin{equation}\label{eqrel}
        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
        \big(\g_i^j(a),y)\big).
\end{equation}
Formally, the axiom states that a set is \emph{uniquely} determined by its
members. It follows that $\thicksim$ defines equality of bids using a static
analysis with respect to equilibrium, where all users who are not changing thier
bids are considered equal.\\
\textbf{Remark:} Equality is both an equivalence relation and a partial order,
and therefore is reflexive, transitive, symmetric and antisymmetric. \\
Now, we may define the mapping $s \mapsto [s]$,
\begin{equation}\label{indeqrel}
         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
\end{equation}o
noting that equality in the bid quantity is implicity satisfied and $z =
\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
buyer-seller pair. Without loss of generality, let $S = \Pi_{j\in\mcI} \big(
\Pi_{i\in\mcI} S_i^j$. The indicator function is the canonical mapping,
$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
topology is preserved, the set of all indicator
functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$.

{
\proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
}\\
\textbf{Proof:}
Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
\overline{P}]^{\vert \mcI^j\vert})$
is a product of closed subsets of compact sets. Now, we have that a closed
subset of a compact set is compact and the resulting product topology gives
Tychonoff's theorem. every product of a
compact space is compact, we have $\g_i \circ B_i^\epsilon$
is compact subset of $B_i^\epsilon$.
 Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
definition of $\Delta$ and the product, 
\begin{align*}
    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
[0,\overline{P}]\bigg)
    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
[0,\overline{P}]\bigg) \\
    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
\times \lambda^j \subset T.
\end{align*}
The result follows from the fact that $t_i$ is continuous in $s_i$, as was
proven in \cite{semret}, and as a finite union of compact sets is a compact set.
$\qed$
on any subset $\lbrace
s_{-i}\in S_i : \ \forall \ z > 0, \overline{P} \ge P_i(z,s_{-i}) \ge
\underline{P} \rbrace$, where $0<\underline{P}\le \overline{P} < \infty$
(HERE) The dimension of a linear space is defined as the maximal number of linearly
independent vectors or, equivalently, as the minimal number of vectors that span
the space

%We have proven that buyers will submit bids according to their marginal
%valuations. Now, in the interest of completeness (BAD SENTENCE), 
We have that all bids represent $\epsilon$-best replies, and, as was proven in
\cite{lazar}, the sellers' positive reserve price implies that bids are
truthful. Finally, by properties determined by the construction of a mixed strategy
symmetric game with a 2-dimensional message space, we may now restrict our
analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.

@@

We show that our bidding strategy is
part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
equilibrium, where the sellers reserve prices are fixed.
{
\lemma{(Static Nash Equilibrium)} 
Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
Using the rules of the data auction mechanism applied independently by each
user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
}\\
\textbf{Proof:}
(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
and we may use Brouwer's fixed point theorem, as in \cite{semret},

@@

The rules of the PSP
multi-auction drive market mutations that evolve and are regulated by the user
strategies.
(HERE)
